Cellular Automata and Computational Universality

### 2018-09-21 paper/paper.tex
Poster finished, elementary automata improved

\section{Introduction}
    A cellular automaton is a discrete model of computation which consists of a
    finite collection of ``cells'', each in one of a finite number of states.
    The state of each of these cells may evolve over the progression of time in
    discrete steps, and may do so according to a deterministic set of rules
    based on the states of neighbouring cells. Their inherently discrete nature
    allows for strong analogies to be made with digital computers, and gifts
    them the ability to simulate digital processes and the potential to solve
    problems in this area.

>>>>

\section{Introduction}
    A cellular automaton is a discrete model of computation which consists of a
    finite collection of ``cells'', each in one of a finite number of states.
    The state of each of these cells may evolve over the progression of time in
    discrete steps, and may do so according to a deterministic set of rules
    based on the states of neighbouring cells. Their inherently discrete nature
    allows for strong analogies to be made with digital computers, and gifts
    them the ability to simulate digital processes and the potential to solve
    a range of problems in this area.
